Global Value Chain Analysis of LMICs

### 2015-04-22 OECD-TiVa-LMIC-GVCs.Rmd
final version

 ```{r, echo=FALSE, warnings=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")
load("data/trca.RData")

@@

## New Toolbox and Indicators: decompr and gvc

@@

@@

 ```{r, tidy=FALSE}
 library(decompr)
 ls.str("package:decompr")
 ```

 ```{r, tidy=FALSE}
 library(gvc)
 ls.str("package:gvc")
 ```

@@

Motor and Transport Equipment: Traditional underestimation

@@

  - new indicators suited for non-traditional trade patterns
  - non-trivial linear algebra involved
  - simplified application of mew algorithms
  - many more indicators and tools available in the packages
    - decompr: decomposition
    - gvc: analysis

>>>>

 ```{r, echo=FALSE, warnings=FALSE, message=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")
load("data/trca.RData")

@@

Decompositions

 - Leontief (post: exports / output)
 - new Wang-Wei-Zhu algorithm

 - citation info

 ```{r, tidy=FALSE}
 library(decompr)
 ```

@@

 - no citation info (yet!)

@@

# Trends in GVCs

@@

Motor and Transport Equipment in Thailand: Traditional underestimation

@@

  - new indicators suited for non-traditional trade patterns
  - non-trivial linear algebra involved
  - simplified application of new algorithms
  - many more indicators and tools available in the packages
    - decompr: decomposition
    - gvc: analysis
